`r paste(params$species)` climatic and biotic velocities for `r paste(params$region)` (immature: `r paste(params$immature)`

### 2020-01-24 analysis/VOCC/4-vocc-biotic.Rmd
scramble all spp and regions individually

glimpse (d)
if (scrambled_years) {
  d2 <- list()

  set.seed(9999) 
  # set.seed(12345)
  # set.seed(98765) 
  original_years <- unique(d$year)
  new_years <- sample(original_years)
  convert <- cbind(original_years,new_years)
  convert
  for (i in seq_len(length(original_years))) {
    old_year <- as.integer(convert[[i,1]])
    fake_year <- as.integer(convert[[i,2]])
    d2[[i]] <- filter(d, year == old_year) %>% 
      mutate(year = fake_year )
     # browser()
  }
  d <- do.call(rbind, d2)
}
```

@@

grad0 <- plot_vocc(gf0,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "velocity",
  fill_label = "gradient velocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt # no_trans #
) + labs(
  title = "do velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

grad2 <- plot_vocc(gf2,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "velocity",
  fill_label = "gradient velocity",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = sqrt # no_trans # log10 # fourth_root_power # sqrt #
) + labs(
  title = "temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

write.csv(vocc, file = paste0(
  "data/_scrambled3/", age,  "-biotic-vocc-", spp, "-", ssid_string, "-", covs, "-", min(d$year), "-", max(d$year), "-trim10.csv"
))
```

>>>>

glimpse (d)
if (scrambled_years) {
  d2 <- list()
  # set.seed(9999) 
  # set.seed(12345)
  # set.seed(98765) 
  original_years <- unique(d$year)
  new_years <- sample(original_years, replace=F)
  convert <- cbind(original_years, new_years)
  convert
  for (i in seq_len(length(original_years))) {
    old_year <- as.integer(convert[[i,1]])
    fake_year <- as.integer(convert[[i,2]])
    d2[[i]] <- filter(d, year == old_year) %>% 
      mutate(year = fake_year )
     # browser()
  }
  d <- do.call(rbind, d2)
}

convert
```

@@

grad0 <- plot_vocc(gf0,
  # theme_black = TRUE,
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "trend",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "black",
  high_fill = "Steel Blue 4",
  low_fill = "Red 3",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans #
) + labs(
  title = "do velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

grad2 <- plot_vocc(gf2,
  # theme = "black",
  coast = TRUE,
  vec_aes = NULL,
  # grad_vec_aes = "velocity",
  # vec_lwd_range = c(0.5, 0.5),
  NA_label = "NA",
  fill_col = "trend",
  fill_label = "trend",
  raster_alpha = 1,
  # raster_limits = c(raster_min, raster_max),
  na_colour = "white",
  white_zero = TRUE,
  vec_alpha = 0.35,
  axis_lables = FALSE,
  transform_col = no_trans # log10 # fourth_root_power # sqrt #
) + labs(
  title = "temp velocity",
  subtitle = paste0(min(d$year), "-", max(d$year))
)

@@

write.csv(vocc, file = paste0(
  "data/_scrambled5/", age,  "-biotic-vocc-", spp, "-", ssid_string, "-", covs, "-", min(d$year), "-", max(d$year), "-trim10.csv"
))
```
